\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[table]{xcolor}
\usepackage[top = 2.5cm, bottom = 2cm, left = 2.5cm, right = 2.5cm]{geometry}
\usepackage{enumitem}

\title{Group Meeting Report}
\date{}

\begin{document}
\maketitle{}

\section{Agreements}

We all agreed on using Java as the main language for this project.

\subsection{Members and Skills}
\begin{itemize}[leftmargin=2cm]
 \item Nils: Java, GitHub, worked as a full-stack dev
 \item Felipe: Java, GitHub
 \item Erik: Some ML, ANN, General OOP
 \item Pablo: Java, GitHub, various programming languages
 \item Mikel: $Unknown^*$
\end{itemize}

\subsection{Communication}
Our group chose Slack as the official communication channel.

\subsection{CVS and Open Tasks}
GitHub and Git Projects will be used as the versioning system and also to keep track of current and finished tasks.

\subsection{Assistance on Lab Sessions}
No issues with assistance (everyone will attend).

\subsection{Documentation}
JavaDoc will be used as it's a robust and automated solution for this.

\subsection{Code of Conduct}
We all agreed on the following rules:
\begin{itemize}
  \item Not miss deadlines.
  \item Make unit tests for developed functions.
  \item Follow documentation rules for JavaDoc.
  \item Notify if someone can't show up to a group meeting (15 mins before at least).
\end{itemize}

\subsection{Code Conventions}

\vspace{0.5cm}

\begin{itemize}
  \item Camel Case for Functions and Snake Case for variables.
  \item Summarized explanation for functions on comments before it.
  \item New code must pass tests before being merged with the main branch.
  \item Pull-requests must be peer-reviewed and accepted before merging with main branch.
  \item All pull-requests must be linked with an issue.
  \item All issues must have their own cards on Git Projects.
  \item New code must be developed on new branches and not directly on the main branch.
\end{itemize}

\end{document}
